Toward dynamic models of combat or lack thereof in animal mating

### 2015-12-27 ms.tex
some mature equations and table updated.

Need equations for

\begin{itemize}
    \item Populations of ``searching'' males and  ``occupying'' males
    \item Rate at which ``searching'' males encounter empty nests
    \item Rate at which ``searching'' males encounter occupied nests
    \item Rate at which ``occupying'' males abandon an occupied nest
    \item Outcomes of contest between two males
\end{itemize}

@@

I am not sure if this is the way to do this, 
or if there is a way to do it with refs (?)
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $m$ & $kg$ & mass\\
        \hline
    \end{tabular}
\end{table}

>>>>

/* this is just for consideration I am not sure if it will be needed or useful */
Number of mature males at time $t$:
\begin{equation} \label{eq:num_mature}
    K_{mature}(t) = \lfloor{K_{initial}(Pr({\rm mature} \, | m(t)) - S(t))}\rfloor
\end{equation}
A searching individual could encounter nests at a rate equal to its ``exploration trait'' $\lambda_i$:
\begin{equation} \label{eq:encounter rate}
    {\rm Encounters} = \lfloor\lambda_it_{searching}\rfloor
\end{equation}
/* end */

Need equations for:
\begin{itemize}
    \item Populations of ``searching'' males and  ``occupying'' males
    \item Rate at which ``searching'' males encounter empty nests
    \item Rate at which ``searching'' males encounter occupied nests
    \item Rate at which ``occupying'' males abandon an occupied nest
    \item Outcomes of contest between two males
\end{itemize}

@@

I am not sure if this is the way to do this, 
or if there is a way to do it with refs (?)
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $kg$ & mass\\
        $m_mat$ & $kg$ & The size at which 50\% of the population is mature.\\ 
        \hline
    \end{tabular}
\end{table}
